%******************************************************************************
% Preamble
%******************************************************************************
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{lscape}
\usepackage{verbatim}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[left]{lineno}
\usepackage[pdftex]{color}
\usepackage{subfigure}
\usepackage[labelsep=period,labelfont={bf},textfont={normal}]{caption}
\usepackage{comment}
\usepackage{enumitem}

\definecolor{myr}{rgb}{0.6,0,0}
\definecolor{myb}{rgb}{0,0,0.6}
\definecolor{myg}{rgb}{0,0.4,0}

\usepackage{hyperref}
\hypersetup{colorlinks,
    citecolor=blue,
    filecolor=blue,
    linkcolor=blue,
     urlcolor=blue}
     
\setlength{\parskip}{1.5ex}
\setlength{\parindent}{0em}

\geometry{left=1in,right=1in,top=1in,bottom=1in}

\lhead{}
\chead{}
\rhead{\scshape{davide pettenuzzo---vitae}}

\lfoot{}
\cfoot{\thepage\ of \pageref{LastPage}}
\rfoot{\emph{\today}}

\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

\onehalfspacing
\pagestyle{fancy}
%******************************************************************************
% Document starts here
%******************************************************************************
\begin{document}
%------------------------------------------------------------------------------
\begin{center}
\textbf{DAVIDE PETTENUZZO} \\
International Business School, Brandeis University \\
415 South Street, MS 032\\
Waltham, MA 02453-2728 \\
phone: (781) 736-2834 \\
email: \href{mailto:dpettenu@brandeis.edu}{\nolinkurl{dpettenu@brandeis.edu}} \\
website: \url{https://davidepettenuzzo.com} \\
\end{center}
\hrule 

\bigskip

%%------------------------------------------------------------------------------
%\underline{\textbf{Personal}}\\
%Date of birth: November 4th, 1975. \\
%Citizenship: Italian, U.S. \\
%Married with two children. \\
%Lives in Newton, Massachusetts. \\ \\ 
%------------------------------------------------------------------------------
\vspace{0.15in}

\underline{\textbf{Employment}}\\

May 2022 -- present, Professor  of Financial Econometrics\\
\hspace*{10mm} \underline{Brandeis International Business School}

July 2019 -- April 2022, Associate Professor  of Financial Econometrics\\
\hspace*{10mm} \underline{Brandeis International Business School}

April 2018 -- June 2019, Associate Professor (tenured) \\
\hspace*{10mm} Department of Economics, \underline{Brandeis University}

July 2011 -- March 2018, Assistant Professor \\
\hspace*{10mm} Department of Economics, \underline{Brandeis University}
 
Ocotber 2005 -- June 2011, Consultant (Antitrust Practice)\\
\hspace*{10mm} \underline{Bates White LLC} (Economic Consulting)

\underline{\textbf{Visiting positions}}\\
%Fall 2020--2023, Visiting  Professor\\
%\hspace*{10mm} \underline{Harvard University}, %Department of Economics 

July -- August 2018 \& February--June 2023: Visiting Fellow\\ 
\hspace*{10mm} \underline{Collegio Carlo Alberto}\\

%\newpage
\underline{\textbf{Education}}\\
Ph.D., Economics, Bocconi University, Milan (Italy), 2005.\\
Visiting graduate student, University of California, San Diego, 2002-2005. \\
M.A. (Master of Arts), Economics, CORIPE Piemonte, Turin (Italy), 2001. \\
B.Sc., Economics, University of Verona, Italy, 2000.\\
%------------------------------------------------------------------------------
\newpage
\underline{\textbf{Published and Forthcoming Articles}}
\begin{enumerate}	
	
			\item Conditional Forecasts in Large Bayesian VARs with Multiple Equality and Inequality Constraints, with Joshua Chan, Aubrey Poon and Dan Zhou, \textbf{Journal of Economic Dynamics and Control}, 173 (2025).
	
			\item ``Payout suspensions during the Covid-19 pandemic'', 	with Allan Timmermann and Riccardo Sabbatucci, \textbf{Economics Letters}, 224 (2023).
		
			\item ``Dividend Suspensions and Cash Flows During the Covid-19 Pandemic: A Dynamic Econometric Model'', with Allan Timmermann and Riccardo Sabbatucci, \textbf{Journal of Econometrics}, 235, pp.1522--1541 (2023).
	
		\item ``Corrigendum to “Predictability of stock returns and asset allocation under structural breaks” [J. Econometrics 164 (2011) 60–78]'', with Yong Song and Allan Timmermann \textbf{Journal of Econometrics}, 227, pp. 513--517 (2022).
	
		\item ``Machine learning econometrics: Bayesian algorithms and methods'', with Dimitris Korobilis, \textbf{Oxford Research Encyclopedia: Economics and Finance}, (2020).
	
		\item ``Cash Flow News and Stock Price Dynamics'', with Allan Timmermann and Riccardo Sabbatucci, \textbf{Journal of Finance}, 75, pp. 2221--2270  (2020).
		
		\item ``Optimal Asset Allocation with Multivariate Bayesian Dynamic Linear Models'', with Carlos Carvahlo and Jared Fisher, \textbf{Annals of Applied Statistics}, 14, pp. 299--338 (2020).
		
		\item ``Forecasting Stock Returns: A Predictor-constrained Approach'', with Zhiyuan Pan and Yudong Wang, \textbf{Journal of Empirical Finance}, 55, pp. 200--217 (2020).
		
		\item ``Adaptive Hierarchical Priors for High-Dimensional Vector Autoregressions'', with Dimitris Korobilis, \textbf{Journal of Econometrics}, 212, pp. 241--271 (2019).
		
		\item ``Bayesian Compressed VARs'', with Gary Koop and Dimitris Korobilis, \textbf{Journal of Econometrics}, 210, pp. 135--154 (2019).
		
		\item ``Bond Return Predictability: Economic Value and Links to the Macroeconomy'', with Antonio Gargano and Allan Timmermann, \textbf{Management Science}, 65, pp. 508--540 (2019).
	\item ``Option-Implied Equity Premium Predictions via Entropic Tilting'', with Konstantinos Metaxoglou  and Aaron Smith -- \textbf{Journal of Financial Econometrics}, 17, pp. 559--586  (2018).
	
		  \item ``Forecasting Macroeconomic Variables Under Model Instability'', with Allan Timmermann, \textbf{Journal of Business \& Economic Statistics}, 35, pp. 183--201  (2017). 
	\item ``A MIDAS Approach to Modeling First and Second Moment Dynamics'', with Allan Timmermann and Rossen Valkanov, \textbf{Journal of Econometrics}, 193, pp. 315-334 (2016).
	\item ``Optimal Portfolio Choice under Decision-Based Model Combinations'', with Francesco Ravazzolo - \textbf{Journal of Applied Econometrics}, 31, pp. 1312--1332 (2016).
	\item ``Forecasting Stock Returns under Economic Constraints'', with Allan Timmermann and Rossen Valkanov, \textbf{Journal of Financial Economics}, 114, pp. 517--553 (2014). 
	\item ``Granger Causality, Exogeneity, Cointegration, and Economic Policy Analysis'', with Halbert White, \textbf{Journal of Econometrics}, 178, pp. 316--330 (2014). 
	\item ``Predictability of Stock Returns and Asset Allocation under Structural Breaks'', with Allan Timmermann, \textbf{Journal of Econometrics}, 164, pp. 60--78 (2011). 
	\item ``Learning, Structural Instability, and Present Value Calculations'', with Allan Timmermann and Hashem Pesaran, \textbf{Econometric Reviews}, 26, pp. 253--288 (2007). 
	\item ``Forecasting Time Series subject to Structural Breaks'', with Allan Timmermann and Hashem Pesaran, \textbf{Review of Economic Studies}, 73, pp. 1057--1084 (2006). 

		\newcounter{enumTemp}
    \setcounter{enumTemp}{\theenumi}
 \end{enumerate}
%------------------------------------------------------------------------------
\underline{\textbf{Current Working Papers}}
\begin{enumerate}[resume]
	
	\item ``Modeling and Forecasting Count Data with Vector Autoregressions'', with Aubrey Poon and Dan Zhu
	
	\item ``Financial Statements and Macroeconomic Dynamics'', with Allan Timmermann and Riccardo Sabbatucci
	
	\item ``Macroeconomic Forecasting with Large Language Models'', with Andrea Carriero and Shubhranshu Shekhar
	
	\item ``Outlasting the Pandemic: Corporate Payout and Financing Decisions During Covid-19'', with Allan Timmermann and Riccardo Sabbatucci
	
	\item ``The Term Structure and Cross-section of Cash Flow Risk'', with Riccardo Sabbatucci, \textbf{receiver of INQUIRE 2020 Europe Research Grant} 
\end{enumerate}
%\newpage 
\underline{\textbf{Work in Progress}}
\begin{enumerate}[resume]
		\item ``Double Descent and Benign Overfitting in Macroeconomic Forecasting'', with Andrea Carriero and Florian Huber
	\item ``MacroCast: A Vintage-Consistent Time Series Foundation Model for Real-Time Macroeconomic Forecasting'', with Andrea Carriero and Shubhranshu Shekhar
	\item ``Modeling Stock-Bond Correlations'', with Gregor Kastner and Allan Timmermann
	
	
\end{enumerate}
%\newpage
%------------------------------------------------------------------------------
\underline{\textbf{Teaching}}
\begin{itemize}
	\item Brandeis
	\begin{itemize}
		\item Econometrics (Undergraduate).
		\item Financial Economics (Undergraduate). 
		\item Applied Econometrics with R (M.A. in Business Analytics) 
		\item Advanced Econometrics (Ph.D.)
	\end{itemize}
\item Harvard
	\begin{itemize}
		\item Introduction to Econometrics (Undergraduate)
	\end{itemize}
\end{itemize}
%------------------------------------------------------------------------------
\underline{\textbf{Ph.D. Students advised}} \\ \\
\underline{Committee chair}: 
\begin{itemize}
	\item Cansu Isler (in progress), Yuanhui Li (2026), Yufei Zhang (2025, first job: Acadian Asset Management), Mark McAvoy (2021, first job: Research Scientist, Afiniti)
\end{itemize}	
\underline{Committee Member}: 
\begin{itemize}
	\item Kris Gado (completed), Karen Smith (2023, first job: Drew University), Mengnan Zhu (2022, first job:  Dickinson College), Jared Fisher (UT Austin, first job: University of California Berkeley, Department of Statistics), Raffi Garcia  (2018, first job: Rensselaer Polytechnic Institute - New York), Jeremy Kronick (2015, first job: C.D. Howe Institute - Toronto), Xia Meng (2012; first job: Bates White, LLC - DC). 
\end{itemize}
%------------------------------------------------------------------------------
\underline{\textbf{Undergraduate Students advised}} \\ \\
\underline{Committee chair}: 
\begin{itemize}
	\item Matthew Etkins (2020); Benjamin Shaiman (2019); Saul Cohen (2018); George Velonias (2017); Xavier Bautista (2015); Yosef Schafell (2013); Tarun Badia (2012). 
\end{itemize}
\underline{Committee Member}: 
\begin{itemize}
	\item Maxie Phung (2020); Aria Pradhan (2020); Lynn Sun (2016); Justin Kim (2015); Toma Cubrilo (2014).
\end{itemize}

%------------------------------------------------------------------------------
%\newpage
\underline{\textbf{Fellowships and Awards}}
\begin{itemize}
\item Fellow of the International Association of Applied Econometrics, 2025	
\item Honoree, Brandeis Senior Week Faculty \& Staff Appreciation Event, 2017	 
%Recognized by seniors as having “assisted, mentored, and inspired them throughout their time at Brandeis.”, 2018
\item Inquire Europe Research Grant, 2018 and 2020
\item Brandeis University Research Innovation Awards, 2016. 
\item Theodore and Jane Norman Fund for Faculty Research and Creative Projects, 2013, 2015, 2016, 2017. 
\item Kermit H. Perlmutter Fellowship Award for Teaching Excellence, 2014. 
\end{itemize}
%------------------------------------------------------------------------------
\underline{\textbf{Conference and Seminar Presentations}}
\begin{itemize}
	\item 2026: IMF AI Lab (virtual), UNC Charlotte (scheduled)
	\item 2025: Virtual Time Series Seminar (virtual), University of Washington, NBER Summer Institute, IAAE
		\item 2024: NBER-NSF Time series conference, AMLEDS (virtual), Greenline Workshop in Econometrics
	\item 2023: University of Padova, University of Glasgow, Ca' Foscari Workshop on Advanced Econometrics for High-frequency Data
	\item 2022: University of Nottingham (virtual), Queen Mary University of London (virtual)
	\item 2021: North American Summer Meeting of the Econometric Society (virtual) 
	\item 2019: McCombs School of Business (UT Austin), St. Louis Fed Applied Time Series Econometrics Workshop, European Seminar on Bayesian Econometrics (University of St. Andrews, UK)
	\item 2018: University of Southern California, IAAE 2018 Annual Conference, NBER-NSF Time Series Conference (UC San Diego);
	\item 2017: Collegio Carlo Alberto (Turin, Italy), Big Data in Predictive Dynamic Econometric Modeling (University of Pennsylvania), NBER-NSF SBIES Meeting (Washington University, St. Louis), 23rd International Conference Computing in Economics and Finance (New York), Brown University;
	\item 2016: University of Pennsylvania, IAAE 2016 Annual Conference, NBER Summer Institute Workshop on Forecasting and Empirical Methods in Macro and Finance, European Meeting of the Econometric Society;
  \item 2015: NBER-NSF SBIES Meeting (Washington University, St. Louis), Federal Reserve Bank of Boston, The University of Texas, McCombs School of Business, SOFIE Meeting (Aarhus, Denmark), European Seminar on Bayesian Econometrics (Gerzensee, Switzerland), University of Illinois Urbana-Champaign;
	\item 2014: Computational and Financial Econometric conference (Pisa Italy), $EC^2$ conference - Advances in Forecasting (Barcelona, Spain),  Carleton University \& Bank of Canada (Ottawa, Canada), ASSA meeting -- Econometric Society session (Philadelphia);  
	\item 2013: Boston University, Western Finance Association meeting (Lake Tahoe), Econometric Society Summer Institute (USC), European Seminar on Bayesian Econometrics (Oslo, Norway); 
	\item 2011: Brandeis University, University of Massachusetts Amherst; 
	\item 2006: Bates White LLC -- Antitrust Conference, SUNY Albany, CEMFI Madrid, Bank of Canada.
\end{itemize}

%------------------------------------------------------------------------------
\underline{\textbf{Professional Activities}}
\begin{description}
	
\item \textit{Associate Editor}, Journal of Financial Econometrics, July 2015--present. 
\item \textit{Associate Editor}, Journal of Business \& Economic Statistics, January 2016--December 2020.

\item \emph{Referee} for Econometrica, Review of Economics and Statistics, Journal of the American Statistical Association, Journal of Econometrics, Journal of Applied Econometrics, Journal of Business and Economic Statistics, International Journal of Forecasting, Economics Letters, Journal of Finance, Review of Financial Studies, Management Science, Journal of Financial Econometrics, Quarterly Review of Economics and Finance, Studies in Economics and Finance, Studies in Nonlinear Dynamics \& Econometrics, Annals of Applied Statistics.

\item \emph{Conference Committees}: International Association for Applied Econometrics (2016--2024), The Society for Nonlinear Dynamics and Econometrics Annual symposium (Paris, March 2016), 8th International Conference on Computational and Financial Econometrics (Pisa, 2014).

\item\emph{Member} of American Economic Association, Western Finance Association, Econometric Society, Society for Financial Econometrics (SoFiE), Computational and Financial Econometrics (CFE) network, The Euro Area Business Cycle Network.

\item \emph{Reviewer} for the Italian National Agency for the Evaluation of Universities and Research Institutes (ANVUR) 
\end{description}
 
\end{document}
%EOF