%******************************************************************************
% Preamble
%******************************************************************************
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{lscape}
\usepackage{verbatim}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[left]{lineno}
\usepackage[pdftex]{color}
\usepackage{subfigure}
\usepackage[labelsep=period,labelfont={bf},textfont={normal}]{caption}
\usepackage{comment}

\definecolor{myr}{rgb}{0.6,0,0}
\definecolor{myb}{rgb}{0,0,0.6}
\definecolor{myg}{rgb}{0,0.4,0}

\usepackage{hyperref}
\hypersetup{colorlinks,
    citecolor=blue,
    filecolor=blue,
    linkcolor=blue,
     urlcolor=blue}
     
\setlength{\parskip}{1.5ex}
\setlength{\parindent}{0em}

\geometry{left=1in,right=1in,top=1in,bottom=1in}

\lhead{}
\chead{}
\rhead{\scshape{davide pettenuzzo---vitae}}

\lfoot{}
\cfoot{\thepage\ of \pageref{LastPage}}
\rfoot{\emph{December 5, 2013}}}

\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

\onehalfspacing
\pagestyle{fancy}
%******************************************************************************
% Document starts here
%******************************************************************************
\begin{document}
%------------------------------------------------------------------------------
\begin{center}
\textbf{DAVIDE PETTENUZZO} \\
Department of Economics, Brandeis University \\
415 South Street, MS 021 \\
Waltham, MA 02453-2728 \\
phone: (781) 736-2834 \\
email: \href{mailto:dpettenu@brandeis.edu}{\nolinkurl{dpettenu@brandeis.edu}} \\
website: \url{http://people.brandeis.edu/~dpettenu} \\
\end{center}
\hline 
\bigskip

%------------------------------------------------------------------------------
\underline{\textbf{Personal}}\\
Date of birth: November 4th, 1975. \\
Citizenship: Italian, U.S. \\
Married with two children, Leonardo (5) and Tommaso (6 months). \\
Lives in Newton, Massachusetts. \\ \\ 
%------------------------------------------------------------------------------
\underline{\textbf{Education}}\\
Ph.D., Economics, Bocconi University, Milan (Italy), 2005.\\
M.A. (Master of Arts), Economics, CORIPE Piemonte, Turin (Italy), 2001. \\
B.Sc., Economics, University of Verona, Italy, 2000.\\
Visiting graduate student, University of California, San Diego, 2002-2005. \\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Employment}}\\
Assistant Professor, Department of Economics, Brandeis University, 2011-present.\\
Manager, Bates White LLC (Antitrust Practice), San Diego CA, 2007-2011.\\
Senior Consultant, Bates White LLC (Antitrust Practice), San Diego CA, 2005-2007. \\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Fields of Interest}}\\
Time-series econometrics, Bayesian econometrics, Forecasting, Empirical finance.\\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Publications}}
\begin{enumerate}	
	\item ``Forecasting Stock Returns under Economic Constraints'', with Allan Timmermann and Rossen Valkanov, \emph{Journal of Financial Economics} (forthcoming)
	
	\item ``Granger Causality, Exogeneity, Cointegration, and Economic Policy Analysis'', with Halbert White, \emph{Journal of Econometrics}, 178, pp. 316--330 (2014).
	
	\item ``Predictability of Stock Returns and Asset Allocation under Structural Breaks'', with Allan Timmermann, \emph{Journal of Econometrics}, 164, pp. 60--78 (2011). \\
	\underline{Number of citations:} 36 (\emph{Source: Google Scholar})
	
	\item ``Learning, Structural Instability, and Present Value Calculations'', with Allan Timmermann and Hashem Pesaran, \emph{Econometric Reviews}, 26, pp. 253--288 (2007). \\
	\underline{Number of citations:} 23 (\emph{Source: Google Scholar})

	\item ``Forecasting Time Series subject to Structural Breaks'', with Allan Timmermann and Hashem Pesaran, \emph{Review of Economic Studies}, 73, pp. 1057--1084 (2006). \\
	\underline{Number of citations:} 154 (\emph{Source: Google Scholar})

		\newcounter{enumTemp}
    \setcounter{enumTemp}{\theenumi}
 \end{enumerate}
%------------------------------------------------------------------------------
\underline{\textbf{Current Working Papers and Work in Progress}}
\begin{enumerate}
	\setcounter{enumi}{\theenumTemp}
	\item ``Model Instabilities in Predictive Regressions of U.S. Stock Returns'', with Massimo Guidolin and Francesco Ravazzolo.
	\item ``Busts and Booms in Oil Prices'', with Konstantinos Metaxoglou  and Aaron Smith.
	\item ``Predicting Distress Risk using Dynamic Logisitic Regressions with Time Varying Parameters'' (tentative title), with Jens Hilscher and Pulak Ghosh.
\end{enumerate}

%------------------------------------------------------------------------------
\underline{\textbf{Teaching}}\\
Econometrics (undergraduate).\\
Financial Economics (undergraduate). \\
Advanced Econometrics (Ph.D.). \\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Ph.D. Students advised}} \\ \\
\underline{Committee Member}: 
\begin{itemize}
	\item Jeremy Kronick (expected 2014);
	\item Xia Meng (2012; first job: Bates White, LLC). 
\end{itemize}
%------------------------------------------------------------------------------
\clearpage
\underline{\textbf{Undergraduate Students advised}} \\ \\
\underline{Committee chair}: 
\begin{itemize}
	\item Yosef Schafell (2013);
	\item Tarun Badia (2012). 
\end{itemize}

%------------------------------------------------------------------------------
\underline{\textbf{Fellowships and Awards}}\\
Theodore and Jane Norman Fund for Faculty Research and Creative Projects, 2013. \\
Brandeis Start up Grant, 2011. \\
Ph.D. student Tuition Fellowship, Bocconi University, 2001-2005.\\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Conference and Seminar Presentations}}\\
ASSA meeting, Econometric Society session, 2014 (scheduled); Boston University, 2013 (scheduled); Western Finance Association meeting, 2013; Econometric Society Summer Institute, 2013; European Seminar on Bayesian Econometrics, 2013; Brandeis University, 2011; University of Massachusetts Amherst, 2011; Bates White LLC, Antitrust Conference, 2006; Bates White LLC, 2005; SUNY Albany, 2005; Eviews, 2005; CEMFI Madrid, 2005; Bank of Canada, 2005.\\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Professional Activities}}
\begin{description}
	\item\emph{Member} of American Economic Association, Western Finance Association, Econometric Society, European Economic Association, European Finance Association.

\item \emph{Referee} for Econometrica, Review of Economics and Statistics, Economics Letters, Journal of Applied Econometrics, Journal of Business and Economic Statistics, Journal of Econometrics, Review of Financial Studies, Journal of Financial Econometrics, Quarterly Review of Economics and Finance, Studies in Economics and Finance.

\item \emph{Reviewer} for the Italian National Agency for the Evaluation of Universities and Research Institutes (ANVUR) 
\end{description}
 
\end{document}
%EOF