%******************************************************************************
% Preamble
%******************************************************************************
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{lscape}
\usepackage{verbatim}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[left]{lineno}
\usepackage[pdftex]{color}
\usepackage{subfigure}
\usepackage[labelsep=period,labelfont={bf},textfont={normal}]{caption}
\usepackage{comment}

\definecolor{myr}{rgb}{0.6,0,0}
\definecolor{myb}{rgb}{0,0,0.6}
\definecolor{myg}{rgb}{0,0.4,0}

\usepackage{hyperref}
\hypersetup{colorlinks,
    citecolor=blue,
    filecolor=blue,
    linkcolor=blue,
     urlcolor=blue}
     
\setlength{\parskip}{1.5ex}
\setlength{\parindent}{0em}

\geometry{left=1in,right=1in,top=1in,bottom=1in}

\lhead{}
\chead{}
\rhead{\scshape{davide pettenuzzo---vitae}}

\lfoot{}
\cfoot{\thepage\ of \pageref{LastPage}}
\rfoot{\emph{November 5, 2015}}

\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

\onehalfspacing
\pagestyle{fancy}
%******************************************************************************
% Document starts here
%******************************************************************************
\begin{document}
%------------------------------------------------------------------------------
\begin{center}
\textbf{DAVIDE PETTENUZZO} \\
Department of Economics, Brandeis University \\
415 South Street, MS 021 \\
Waltham, MA 02453-2728 \\
phone: (781) 736-2834 \\
email: \href{mailto:dpettenu@brandeis.edu}{\nolinkurl{dpettenu@brandeis.edu}} \\
website: \url{http://people.brandeis.edu/~dpettenu} \\
\end{center}
\hline 
\bigskip

%------------------------------------------------------------------------------
\underline{\textbf{Personal}}\\
Date of birth: November 4th, 1975. \\
Citizenship: Italian, U.S. \\
Married with two children, Leonardo and Tommaso. \\
Lives in Newton, Massachusetts. \\ \\ 
%------------------------------------------------------------------------------
\underline{\textbf{Education}}\\
Ph.D., Economics, Bocconi University, Milan (Italy), 2005.\\
Visiting graduate student, University of California, San Diego, 2002-2005. \\
M.A. (Master of Arts), Economics, CORIPE Piemonte, Turin (Italy), 2001. \\
B.Sc., Economics, University of Verona, Italy, 2000.\\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Professional Appointments}}\\
Assistant Professor, Department of Economics, Brandeis University, 2011--present.\\
Associate Editor, \textit{Journal of Financial Econometrics}, 2015--present.

\underline{Bates White LLC} (Economic Consulting, San Diego CA)\\
Manager, (Antitrust Practice), 2007--2011.\\
Senior Consultant (Antitrust Practice), 2005--2007. \\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Fields of Interest}}\\
Time-series econometrics, Bayesian econometrics, Forecasting, Empirical finance.\\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Published Articles}}
\begin{enumerate}	

	\item ``Optimal Portfolio Choice under Decision-Based Model Combinations'', with Francesco Ravazzolo - \textbf{Journal of Applied Econometrics}, \textit{forthcoming}.
	
	\item ``A MIDAS Approach to Modeling First and Second Moment Dynamics'', with Allan Timmermann and Rossen Valkanov, \textbf{Journal of Econometrics}, \textit{forthcoming}.
	
  \item ``Forecasting Macroeconomic Variables Under Model Instability'', with Allan Timmermann, \textbf{Journal of Business and Economic Statistics},  \textit{forthcoming}. 
		
	\item ``Forecasting Stock Returns under Economic Constraints'', with Allan Timmermann and Rossen Valkanov, \textbf{Journal of Financial Economics}, 114, pp. 517--553 (2014). \\
	\underline{Number of citations:} 16 (\emph{Source: Google Scholar})
	
	\item ``Granger Causality, Exogeneity, Cointegration, and Economic Policy Analysis'', with Halbert White, \textbf{Journal of Econometrics}, 178, pp. 316--330 (2014). \\
	\underline{Number of citations:} 2 (\emph{Source: Google Scholar})
	
	\item ``Predictability of Stock Returns and Asset Allocation under Structural Breaks'', with Allan Timmermann, \textbf{Journal of Econometrics}, 164, pp. 60--78 (2011). \\
	\underline{Number of citations:} 57 (\emph{Source: Google Scholar})
	
	\item ``Learning, Structural Instability, and Present Value Calculations'', with Allan Timmermann and Hashem Pesaran, \textbf{Econometric Reviews}, 26, pp. 253--288 (2007). \\
	\underline{Number of citations:} 28 (\emph{Source: Google Scholar})

	\item ``Forecasting Time Series subject to Structural Breaks'', with Allan Timmermann and Hashem Pesaran, \textbf{Review of Economic Studies}, 73, pp. 1057--1084 (2006). \\
	\underline{Number of citations:} 218 (\emph{Source: Google Scholar})

		\newcounter{enumTemp}
    \setcounter{enumTemp}{\theenumi}
 \end{enumerate}
%------------------------------------------------------------------------------
\underline{\textbf{Current Working Papers and Work in Progress}}
\begin{enumerate}
	\setcounter{enumi}{\theenumTemp}
	\item ``Bond Return Predictability: Economic Value and Links to the Macroeconomy'', with Antonio Gargano and Allan Timmermann.
	\item ``Exponential Tilting with Variance Risk Premia: Equity Premium and Oil Prices'', with Konstantinos Metaxoglou  and Aaron Smith.
	\item ``Bayesian Compressed VARs'', with Gary Koop and Dimitris Korobilis.
	\item ``Strategic Asset Allocation: A Time-Varying Predictive Approach'', with Carlos Carvahlo and Jared Fisher 
	\item ``Parameter Uncertainty and Valuations, with Pierluigi Balduzzi.
	
\end{enumerate}

%------------------------------------------------------------------------------
\underline{\textbf{Teaching}}\\
Econometrics (undergraduate).\\
Financial Economics (undergraduate). \\
Advanced Econometrics (Ph.D.). \\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Ph.D. Students advised}} \\ \\
\underline{Committee Member}: 
\begin{itemize}
	\item Jeremy Kronick (2015, first job: C.D. Howe Institute - Toronto);
	\item Xia Meng (2012; first job: Bates White, LLC - DC). 
\end{itemize}
%------------------------------------------------------------------------------
\underline{\textbf{Undergraduate Students advised}} \\ \\
\underline{Committee chair}: 
\begin{itemize}
	\item Xavier Bautista (2015);
	\item Yosef Schafell (2013);
	\item Tarun Badia (2012). 
\end{itemize}
\underline{Committee Member}: 
\begin{itemize}
	\item Justin Kim (2015);
	\item Toma Cubrilo (2014).
\end{itemize}

%------------------------------------------------------------------------------
\underline{\textbf{Fellowships and Awards}}\\
Theodore and Jane Norman Fund for Faculty Research and Creative Projects, 2015. \\
Kermit H. Perlmutter Fellowship Award for Teaching Excellence, 2014 \\
Theodore and Jane Norman Fund for Faculty Research and Creative Projects, 2013. \\
Brandeis Start up Grant, 2011. \\
Ph.D. student Tuition Fellowship, Bocconi University, 2001-2005.\\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Conference and Seminar Presentations}}
\begin{itemize}
  \item 2015: NBER-NSF SBIES Meeting (Washington University, St. Louis), Federal Reserve Bank of Boston, The University of Texas, McCombs School of Business, SOFIE Meeting (Aarhus, Denmark), ESOBE Annual Conference (Gerzensee, Switzerland), University of Illinois Urbana-Champaign (scheduled);
	\item 2014: Computational and Financial Econometric conference (Pisa Italy), $EC^2$ conference - Advances in Forecasting (Barcelona, Spain),  Carleton University & Bank of Canada (Ottawa, Canada), ASSA meeting -- Econometric Society session (Philadelphia);  
	\item 2013: Boston University, Western Finance Association meeting (Lake Tahoe), Econometric Society Summer Institute (USC), European Seminar on Bayesian Econometrics (Oslo, Norway); 
	\item 2011: Brandeis University, University of Massachusetts Amherst; 
	\item 2006: Bates White LLC -- Antitrust Conference, SUNY Albany, CEMFI Madrid, Bank of Canada.
\end{itemize}

%------------------------------------------------------------------------------
\underline{\textbf{Professional Activities}}
\begin{description}
\item\emph{Member} of American Economic Association, Western Finance Association, Econometric Society, Computational and Financial Econometrics (CFE) network, The Euro Area Business Cycle Network.

\item \emph{Referee} for Econometrica, Review of Economics and Statistics, Journal of the American Statistical Association, Journal of Econometrics, Journal of Applied Econometrics, Journal of Business and Economic Statistics, International Journal of Forecasting, Economics Letters, Journal of Finance, Review of Financial Studies, Journal of Financial Econometrics, Quarterly Review of Economics and Finance, Studies in Economics and Finance, Studies in Nonlinear Dynamics & Econometrics.

\item \emph{Reviewer} for the Italian National Agency for the Evaluation of Universities and Research Institutes (ANVUR) 
\end{description}
 
\end{document}
%EOF