%******************************************************************************
% Preamble
%******************************************************************************
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{lscape}
\usepackage{verbatim}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[left]{lineno}
\usepackage[pdftex]{color}
\usepackage{subfigure}
\usepackage[labelsep=period,labelfont={bf},textfont={normal}]{caption}
\usepackage{comment}

\definecolor{myr}{rgb}{0.6,0,0}
\definecolor{myb}{rgb}{0,0,0.6}
\definecolor{myg}{rgb}{0,0.4,0}

\usepackage{hyperref}
\hypersetup{colorlinks,
    citecolor=blue,
    filecolor=blue,
    linkcolor=blue,
     urlcolor=blue}
     
\setlength{\parskip}{1.5ex}
\setlength{\parindent}{0em}

\geometry{left=1in,right=1in,top=1in,bottom=1in}

\lhead{}
\chead{}
\rhead{\scshape{davide pettenuzzo---vitae}}

\lfoot{}
\cfoot{\thepage\ of \pageref{LastPage}}
\rfoot{\emph{November 5, 2015}}

\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

\onehalfspacing
\pagestyle{fancy}
%******************************************************************************
% Document starts here
%******************************************************************************
\begin{document}
%------------------------------------------------------------------------------
\begin{center}
\textbf{DAVIDE PETTENUZZO} \\
Department of Economics, Brandeis University \\
415 South Street, MS 021 \\
Waltham, MA 02453-2728 \\
phone: (781) 736-2834 \\
email: \href{mailto:dpettenu@brandeis.edu}{\nolinkurl{dpettenu@brandeis.edu}} \\
website: \url{http://people.brandeis.edu/~dpettenu} \\
\end{center}
\hline 
\bigskip

%------------------------------------------------------------------------------
\underline{\textbf{Personal}}\\
Date of birth: November 4th, 1975. \\
Citizenship: Italian, U.S. \\
Married with two children, Leonardo and Tommaso. \\
Lives in Newton, Massachusetts. \\ \\ 
%------------------------------------------------------------------------------
\underline{\textbf{Education}}\\
Ph.D., Economics, Bocconi University, Milan (Italy), 2005.\\
Visiting graduate student, University of California, San Diego, 2002-2005. \\
M.A. (Master of Arts), Economics, CORIPE Piemonte, Turin (Italy), 2001. \\
B.Sc., Economics, University of Verona, Italy, 2000.\\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Professional Appointments}}\\
Assistant Professor, Department of Economics, Brandeis University, 2011--present.\\
Associate Editor, \textit{Journal of Financial Econometrics}, 2015--present.

\underline{Bates White LLC} (Economic Consulting, San Diego CA)\\
Manager, (Antitrust Practice), 2007--2011.\\
Senior Consultant (Antitrust Practice), 2005--2007. \\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Fields of Interest}}\\
Time-series econometrics, Bayesian econometrics, Forecasting, Empirical finance.\\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Published Articles}}
\begin{enumerate}	

	\item ``Optimal Portfolio Choice under Decision-Based Model Combinations'', with Francesco Ravazzolo - \textbf{Journal of Applied Econometrics}, \textit{forthcoming}.
	
	\item ``A MIDAS Approach to Modeling First and Second Moment Dynamics'', with Allan Timmermann and Rossen Valkanov, \textbf{Journal of Econometrics}, \textit{forthcoming}.
	
  \item ``Forecasting Macroeconomic Variables Under Model Instability'', with Allan Timmermann, \textbf{Journal of Business and Economic Statistics},  \textit{forthcoming}. 
		
	\item ``Forecasting Stock Returns under Economic Constraints'', with Allan Timmermann and Rossen Valkanov, \textbf{Journal of Financial Economics}, 114, pp. 517--553 (2014).
	
	\item ``Granger Causality, Exogeneity, Cointegration, and Economic Policy Analysis'', with Halbert White, \textbf{Journal of Econometrics}, 178, pp. 316--330 (2014). 
	
	\item ``Predictability of Stock Returns and Asset Allocation under Structural Breaks'', with Allan Timmermann, \textbf{Journal of Econometrics}, 164, pp. 60--78 (2011). 
	
	\item ``Learning, Structural Instability, and Present Value Calculations'', with Allan Timmermann and Hashem Pesaran, \textbf{Econometric Reviews}, 26, pp. 253--288 (2007).

	\item ``Forecasting Time Series subject to Structural Breaks'', with Allan Timmermann and Hashem Pesaran, \textbf{Review of Economic Studies}, 73, pp. 1057--1084 (2006). 

		\newcounter{enumTemp}
    \setcounter{enumTemp}{\theenumi}
 \end{enumerate}
%------------------------------------------------------------------------------
\underline{\textbf{Current Working Papers and Work in Progress}}
\begin{enumerate}
	\setcounter{enumi}{\theenumTemp}
	\item ``Bond Return Predictability: Economic Value and Links to the Macroeconomy'', with Antonio Gargano and Allan Timmermann.
	\item ``Exponential Tilting with Variance Risk Premia: Equity Premium and Oil Prices'', with Konstantinos Metaxoglou  and Aaron Smith.
	\item ``Bayesian Compressed VARs'', with Gary Koop and Dimitris Korobilis.
	\item ``Strategic Asset Allocation: A Time-Varying Predictive Approach'', with Carlos Carvahlo and Jared Fisher 
	\item ``Parameter Uncertainty and Valuations, with Pierluigi Balduzzi.
	
\end{enumerate}

%------------------------------------------------------------------------------
\underline{\textbf{Selected consulting experience}}
	
	\begin{itemize}
		\item In the major antitrust litigation, AMD v. Intel, supported plaintiff’s testifying expert by performing econometric analysis to determine the impact of alleged conduct on market shares and prices using a treatment effect approach.
\item Supported multiple testifying experts on behalf of direct and indirect plaintiffs in In re Dynamic Random Access Memory (DRAM) Antitrust Litigation. Serving as the data modeling manager responsible for developing the damages model used to compute purchaser overcharges and damages. Other responsibilities include analyzing and standardizing defendant sale and client purchase data, understanding the DRAM industry, and collecting information on factors that affect DRAM pricing. Also supporting testifying experts on preparation of evidence and testimony for depositions and rebuttal reports.
\item Performed economic and statistical analysis regarding liability and damages on behalf of a large coalition of direct-action plaintiffs in In re Linerboard Antitrust Litigation. Developed an econometric model to calculate production downtime to support the analysis and opinions of the liability expert. Worked with the econometrics team to support settlement and mediation negotiations, discovery, and critique of opposing expert analyses.
\item Supported the causation and damages expert on behalf of the unsecured creditors committee in Enron Corp and Enron North America Corp v. Citigroup Inc. Provided econometric and statistics support for liability analysis and damage apportionment. Used historical trading data to develop a probabilistic model to estimate the date by which Enron would have lost its investment grade status had the company reported its transactions with the bank defendants in a manner reflective of its true economic substance. 
\item Supported analysis presented to the FTC concerning the antitrust implications of The Great Atlantic & Pacific Tea Company’s (A&P) proposed acquisition of Pathmark Stores, Inc. on behalf of the acquiring party. Developed and implemented econometric analysis to evaluate the impact of the entry and exit of over 200 supermarkets, grocery stores, mass merchandisers, clubs, and other retailers of food on prices, margins, and sales. Studied detailed product-level sales information to construct price indices that controlled for possible changes in product mix in order to isolate price effects.
\item Provided statistical and economic analysis on behalf of a major financial institution with multiple prime and subprime mortgage business units. Developed statistical models to detect pricing disparities between protected and unprotected classes. Evaluated mortgage pricing strategies to examine the relationship between pricing and underlying credit risk, and developed alternate risk-adjusted pricing algorithms to reduce pricing disparities.

	\end{itemize}

%------------------------------------------------------------------------------

\underline{\textbf{Teaching}}\\
Econometrics (undergraduate).\\
Financial Economics (undergraduate). \\
Advanced Econometrics (Ph.D.). \\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Fellowships and Awards}}\\
Kermit H. Perlmutter Fellowship Award for Teaching Excellence, 2014 \\
Theodore and Jane Norman Fund for Faculty Research and Creative Projects, 2013. \\
Brandeis Start up Grant, 2011. \\
Ph.D. student Tuition Fellowship, Bocconi University, 2001-2005.\\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Conference and Seminar Presentations}}
\begin{itemize}
  \item 2015: NBER-NSF SBIES Meeting (Washington University, St. Louis), Federal Reserve Bank of Boston, The University of Texas, McCombs School of Business, SOFIE Meeting (Aarhus, Denmark), ESOBE Annual Conference (Gerzensee, Switzerland), University of Illinois Urbana-Champaign (scheduled);
	\item 2014: Computational and Financial Econometric conference (Pisa Italy), $EC^2$ conference - Advances in Forecasting (Barcelona, Spain),  Carleton University & Bank of Canada (Ottawa, Canada), ASSA meeting -- Econometric Society session (Philadelphia);  
	\item 2013: Boston University, Western Finance Association meeting (Lake Tahoe), Econometric Society Summer Institute (USC), European Seminar on Bayesian Econometrics (Oslo, Norway); 
	\item 2011: Brandeis University, University of Massachusetts Amherst; 
	\item 2006: Bates White LLC -- Antitrust Conference, SUNY Albany, CEMFI Madrid, Bank of Canada.
\end{itemize}
%------------------------------------------------------------------------------
\underline{\textbf{Professional Activities}}
\begin{description}
\item\emph{Member} of American Economic Association, Western Finance Association, Econometric Society, European Economic Association, European Finance Association, Computational and Financial Econometrics (CFE) network.

\item \emph{Referee} for Econometrica, Review of Economics and Statistics, Journal of the American Statistical Association, Journal of Econometrics, Journal of Applied Econometrics, Journal of Business and Economic Statistics, International Journal of Forecasting, Economics Letters, Journal of Finance, Review of Financial Studies, Journal of Financial Econometrics, Quarterly Review of Economics and Finance, Studies in Economics and Finance, Studies in Nonlinear Dynamics & Econometrics.


\item \emph{Reviewer} for the Italian National Agency for the Evaluation of Universities and Research Institutes (ANVUR) 
\end{description}
 
\end{document}
%EOF