%******************************************************************************
% Preamble
%******************************************************************************
\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{lscape}
\usepackage{verbatim}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[left]{lineno}
\usepackage[pdftex]{color}
\usepackage{subfigure}
\usepackage[labelsep=period,labelfont={bf},textfont={normal}]{caption}
\usepackage{comment}

\definecolor{myr}{rgb}{0.6,0,0}
\definecolor{myb}{rgb}{0,0,0.6}
\definecolor{myg}{rgb}{0,0.4,0}

\usepackage{hyperref}
\hypersetup{colorlinks,
    citecolor=blue,
    filecolor=blue,
    linkcolor=blue,
     urlcolor=blue}
     
\setlength{\parskip}{1.5ex}
\setlength{\parindent}{0em}

\geometry{left=1in,right=1in,top=1in,bottom=1in}

\lhead{}
\chead{}
\rhead{\scshape{davide pettenuzzo---vitae}}

\lfoot{}
\cfoot{\thepage\ of \pageref{LastPage}}
\rfoot{\emph{December 13, 2016}}

\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

\onehalfspacing
\pagestyle{fancy}
%******************************************************************************
% Document starts here
%******************************************************************************
\begin{document}
%------------------------------------------------------------------------------
\begin{center}
\textbf{DAVIDE PETTENUZZO} \\
Department of Economics, Brandeis University \\
415 South Street, MS 021 \\
Waltham, MA 02453-2728 \\
phone: (781) 736-2834 \\
email: \href{mailto:dpettenu@brandeis.edu}{\nolinkurl{dpettenu@brandeis.edu}} \\
website: \url{http://people.brandeis.edu/~dpettenu} \\
\end{center}
\hline 
\bigskip

%------------------------------------------------------------------------------
\underline{\textbf{Personal}}\\
Date of birth: November 4th, 1975. \\
Citizenship: Italian, U.S. \\
Married with two children, Leonardo and Tommaso. \\
Lives in Newton, Massachusetts. \\ \\ 
%------------------------------------------------------------------------------
\underline{\textbf{Education}}\\
Ph.D., Economics, Bocconi University, Milan (Italy), 2005.\\
Visiting graduate student, University of California, San Diego, 2002-2005. \\
M.A. (Master of Arts), Economics, CORIPE Piemonte, Turin (Italy), 2001. \\
B.Sc., Economics, University of Verona, Italy, 2000.\\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Professional Appointments}}\\
Assistant Professor, Department of Economics, Brandeis University, July 2011--present.

Associate Editor, \textit{Journal of Financial Econometrics}, July 2015--present. \\
Associate Editor, \textit{Journal of Business \& Economic Statistics}, January 2016--present.

\underline{Bates White LLC} (Economic Consulting, San Diego CA)\\
Manager, (Antitrust Practice), 2007--2011.\\
Senior Consultant (Antitrust Practice), 2005--2007. \\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Fields of Interest}}\\
Time-series econometrics, Bayesian econometrics, Forecasting, Empirical finance.\\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Published Articles}}
\begin{enumerate}	

	\item ``A MIDAS Approach to Modeling First and Second Moment Dynamics'', with Allan Timmermann and Rossen Valkanov, \textbf{Journal of Econometrics}, 193, pp. 315-334 (2016).
	\item ``Optimal Portfolio Choice under Decision-Based Model Combinations'', with Francesco Ravazzolo - \textbf{Journal of Applied Econometrics}, 31, pp. 1312--1332 (2016).
	  \item ``Forecasting Macroeconomic Variables Under Model Instability'', with Allan Timmermann, \textbf{Journal of Business \& Economic Statistics},  \textit{In press} (2015). 
	\item ``Forecasting Stock Returns under Economic Constraints'', with Allan Timmermann and Rossen Valkanov, \textbf{Journal of Financial Economics}, 114, pp. 517--553 (2014). 
	\item ``Granger Causality, Exogeneity, Cointegration, and Economic Policy Analysis'', with Halbert White, \textbf{Journal of Econometrics}, 178, pp. 316--330 (2014). 
	\item ``Predictability of Stock Returns and Asset Allocation under Structural Breaks'', with Allan Timmermann, \textbf{Journal of Econometrics}, 164, pp. 60--78 (2011). 
	\item ``Learning, Structural Instability, and Present Value Calculations'', with Allan Timmermann and Hashem Pesaran, \textbf{Econometric Reviews}, 26, pp. 253--288 (2007). 
	\item ``Forecasting Time Series subject to Structural Breaks'', with Allan Timmermann and Hashem Pesaran, \textbf{Review of Economic Studies}, 73, pp. 1057--1084 (2006). 

		\newcounter{enumTemp}
    \setcounter{enumTemp}{\theenumi}
 \end{enumerate}
%------------------------------------------------------------------------------
\underline{\textbf{Current Working Papers and Work in Progress}}
\begin{enumerate}
	\setcounter{enumi}{\theenumTemp}
	\item ``Adaptive Minnesota Prior for High-Dimensional Vector Autoregressions'', with Dimitris Korobilis (December 2016).
	\item ``Option-Implied Equity Premium Predictions via Entropic Tilting'', with Konstantinos Metaxoglou  and Aaron Smith (August 2016) -- \textit{Revise \& Resubmit}, \textbf{Journal of Business \& Economic Statistics}.
	\item ``Bond Return Predictability: Economic Value and Links to the Macroeconomy'', with Antonio Gargano and Allan Timmermann (July 2016) -- \textit{Revise \& Resubmit}, \textbf{Management Science}.
	\item ``Bayesian Compressed VARs'', with Gary Koop and Dimitris Korobilis (April 2016) -- \textit{Revise \& Resubmit}, \textbf{Journal of Econometrics}.
	\item ``Strategic Asset Allocation: A Time-Varying Predictive Approach'', with Carlos Carvahlo and Jared Fisher.
	\item ``High-Frequency Cash Flow News'', with Allan Timmermann and Riccardo Sabbatucci.
	\item ``Parameter Uncertainty and Valuations, with Pierluigi Balduzzi.
	
\end{enumerate}

 
\end{document}
%EOF