%******************************************************************************
% Preamble
%******************************************************************************
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{lscape}
\usepackage{verbatim}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[left]{lineno}
\usepackage[pdftex]{color}
\usepackage{subfigure}
\usepackage[labelsep=period,labelfont={bf},textfont={normal}]{caption}
\usepackage{comment}

\definecolor{myr}{rgb}{0.6,0,0}
\definecolor{myb}{rgb}{0,0,0.6}
\definecolor{myg}{rgb}{0,0.4,0}

\usepackage{hyperref}
\hypersetup{colorlinks,
    citecolor=blue,
    filecolor=blue,
    linkcolor=blue,
     urlcolor=blue}
     
\setlength{\parskip}{1.5ex}
\setlength{\parindent}{0em}

\geometry{left=1in,right=1in,top=1in,bottom=1in}

\lhead{}
\chead{}
\rhead{\scshape{davide pettenuzzo---vitae}}

\lfoot{}
\cfoot{\thepage\ of \pageref{LastPage}}
\rfoot{\emph{April 13, 2017}}

\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

\onehalfspacing
\pagestyle{fancy}
%******************************************************************************
% Document starts here
%******************************************************************************
\begin{document}
%------------------------------------------------------------------------------
\begin{center}
\textbf{DAVIDE PETTENUZZO} \\
Department of Economics, Brandeis University \\
415 South Street, MS 021 \\
Waltham, MA 02453-2728 \\
phone: (781) 736-2834 \\
email: \href{mailto:dpettenu@brandeis.edu}{\nolinkurl{dpettenu@brandeis.edu}} \\
website: \url{http://people.brandeis.edu/~dpettenu} \\
\end{center}
\hline 
\bigskip

%------------------------------------------------------------------------------
\underline{\textbf{Personal}}\\
Date of birth: November 4th, 1975. \\
Citizenship: Italian, U.S. \\
Married with two children. \\
Lives in Newton, Massachusetts. \\ \\ 
%------------------------------------------------------------------------------
\underline{\textbf{Education}}\\
Ph.D., Economics, Bocconi University, Milan (Italy), 2005.\\
Visiting graduate student, University of California, San Diego, 2002-2005. \\
M.A. (Master of Arts), Economics, CORIPE Piemonte, Turin (Italy), 2001. \\
B.Sc., Economics, University of Verona, Italy, 2000.\\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Professional Appointments}}\\
Assistant Professor, Department of Economics, Brandeis University, July 2011--present.

Associate Editor, \textit{Journal of Financial Econometrics}, July 2015--present. \\
Associate Editor, \textit{Journal of Business \& Economic Statistics}, January 2016--present.

\underline{Bates White LLC} (Economic Consulting, San Diego CA)\\
Manager, (Antitrust Practice), 2007--2011.\\
Senior Consultant (Antitrust Practice), 2005--2007. \\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Fields of Interest}}\\
Time-series econometrics, Bayesian econometrics, Forecasting, Empirical finance.\\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Published Articles}}
\begin{enumerate}	
			\item ``Bayesian Compressed VARs'', with Gary Koop and Dimitris Korobilis (February 2017), \textbf{Journal of Econometrics} \textit{(conditionally accepted)}.
	\item ``Bond Return Predictability: Economic Value and Links to the Macroeconomy'', with Antonio Gargano and Allan Timmermann (January 2017), \textbf{Management Science} \textit{(forthcoming)}.
		  \item ``Forecasting Macroeconomic Variables Under Model Instability'', with Allan Timmermann, \textbf{Journal of Business \& Economic Statistics}, 35, pp. 183--201  (2017). 
	\item ``A MIDAS Approach to Modeling First and Second Moment Dynamics'', with Allan Timmermann and Rossen Valkanov, \textbf{Journal of Econometrics}, 193, pp. 315-334 (2016).
	\item ``Optimal Portfolio Choice under Decision-Based Model Combinations'', with Francesco Ravazzolo - \textbf{Journal of Applied Econometrics}, 31, pp. 1312--1332 (2016).
	\item ``Forecasting Stock Returns under Economic Constraints'', with Allan Timmermann and Rossen Valkanov, \textbf{Journal of Financial Economics}, 114, pp. 517--553 (2014). 
	\item ``Granger Causality, Exogeneity, Cointegration, and Economic Policy Analysis'', with Halbert White, \textbf{Journal of Econometrics}, 178, pp. 316--330 (2014). 
	\item ``Predictability of Stock Returns and Asset Allocation under Structural Breaks'', with Allan Timmermann, \textbf{Journal of Econometrics}, 164, pp. 60--78 (2011). 
	\item ``Learning, Structural Instability, and Present Value Calculations'', with Allan Timmermann and Hashem Pesaran, \textbf{Econometric Reviews}, 26, pp. 253--288 (2007). 
	\item ``Forecasting Time Series subject to Structural Breaks'', with Allan Timmermann and Hashem Pesaran, \textbf{Review of Economic Studies}, 73, pp. 1057--1084 (2006). 

		\newcounter{enumTemp}
    \setcounter{enumTemp}{\theenumi}
 \end{enumerate}
%------------------------------------------------------------------------------
\underline{\textbf{Current Working Papers and Work in Progress}}
\begin{enumerate}
	\setcounter{enumi}{\theenumTemp}
	\item ``Adaptive Minnesota Prior for High-Dimensional Vector Autoregressions'', with Dimitris Korobilis (December 2016).
	\item ``Option-Implied Equity Premium Predictions via Entropic Tilting'', with Konstantinos Metaxoglou  and Aaron Smith (August 2016) -- \textit{Revise \& Resubmit}, \textbf{Journal of Business \& Economic Statistics}.
	\item ``Strategic Asset Allocation: A Time-Varying Predictive Approach'', with Carlos Carvahlo and Jared Fisher.
	\item ``High-Frequency Cash Flow News'', with Allan Timmermann and Riccardo Sabbatucci.
	\item ``Parameter Uncertainty and Valuations, with Pierluigi Balduzzi.
	
\end{enumerate}

%------------------------------------------------------------------------------
\underline{\textbf{Teaching}}\\
Econometrics (undergraduate).\\
Financial Economics (undergraduate). \\
Advanced Econometrics (Ph.D.). \\ \\
%------------------------------------------------------------------------------
\underline{\textbf{Ph.D. Students advised}} \\ \\
\underline{Committee Member}: 
\begin{itemize}
	\item Jeremy Kronick (2015, first job: C.D. Howe Institute - Toronto);
	\item Xia Meng (2012; first job: Bates White, LLC - DC). 
\end{itemize}
%------------------------------------------------------------------------------
\underline{\textbf{Undergraduate Students advised}} \\ \\
\underline{Committee chair}: 
\begin{itemize}
	\item George Velonias (2016);
	\item Xavier Bautista (2015);
	\item Yosef Schafell (2013);
	\item Tarun Badia (2012). 
\end{itemize}
\underline{Committee Member}: 
\begin{itemize}
	\item Lynn Sun (2016);
	\item Justin Kim (2015);
	\item Toma Cubrilo (2014).
\end{itemize}

%------------------------------------------------------------------------------
\underline{\textbf{Fellowships and Awards}}\\
\begin{itemize}
\item Brandeis University Research Innovation Awards, 2016. 
\item Theodore and Jane Norman Fund for Faculty Research and Creative Projects, 2013, 2015, 2016. 
\item Kermit H. Perlmutter Fellowship Award for Teaching Excellence, 2014. 
\item Brandeis Start up Grant, 2011. 
\item Ph.D. student Tuition Fellowship, Bocconi University, 2001-2005.
\end{itemize}
%------------------------------------------------------------------------------
\underline{\textbf{Conference and Seminar Presentations}}
\begin{itemize}
	\item 2016: University of Pennsylvania, IAAE 2016 Annual Conference, NBER Summer Institute Workshop on Forecasting and Empirical Methods in Macro and Finance, European Meeting of the Econometric Society;
  \item 2015: NBER-NSF SBIES Meeting (Washington University, St. Louis), Federal Reserve Bank of Boston, The University of Texas, McCombs School of Business, SOFIE Meeting (Aarhus, Denmark), ESOBE Annual Conference (Gerzensee, Switzerland), University of Illinois Urbana-Champaign;
	\item 2014: Computational and Financial Econometric conference (Pisa Italy), $EC^2$ conference - Advances in Forecasting (Barcelona, Spain),  Carleton University & Bank of Canada (Ottawa, Canada), ASSA meeting -- Econometric Society session (Philadelphia);  
	\item 2013: Boston University, Western Finance Association meeting (Lake Tahoe), Econometric Society Summer Institute (USC), European Seminar on Bayesian Econometrics (Oslo, Norway); 
	\item 2011: Brandeis University, University of Massachusetts Amherst; 
	\item 2006: Bates White LLC -- Antitrust Conference, SUNY Albany, CEMFI Madrid, Bank of Canada.
\end{itemize}

%------------------------------------------------------------------------------
\underline{\textbf{Professional Activities}}
\begin{description}

\item \emph{Referee} for Econometrica, Review of Economics and Statistics, Journal of the American Statistical Association, Journal of Econometrics, Journal of Applied Econometrics, Journal of Business and Economic Statistics, International Journal of Forecasting, Economics Letters, Journal of Finance, Review of Financial Studies, Management Science, Journal of Financial Econometrics, Quarterly Review of Economics and Finance, Studies in Economics and Finance, Studies in Nonlinear Dynamics \& Econometrics, Annals of Applied Statistics.

\item \emph{Conference Committees}: 2016 International Association for Applied Econometrics (Sapporo, June 2016), The Society for Nonlinear Dynamics and Econometrics Annual symposium (Paris, March 2016),  2015 International Association for Applied Econometrics (Milan, June 2015), 8th International Conference on Computational and Financial Econometrics (Pisa, 2014).

\item\emph{Member} of American Economic Association, Western Finance Association, Econometric Society, Society for Financial Econometrics (SoFiE), Computational and Financial Econometrics (CFE) network, The Euro Area Business Cycle Network.

\item \emph{Reviewer} for the Italian National Agency for the Evaluation of Universities and Research Institutes (ANVUR) 
\end{description}
 
\end{document}
%EOF